### 2015-06-01 inst/examples/ipm_demostoch_notes.Rmd
adds poisson generator code

>>>>

### Generate correlated Poisson vector
From Yahav and Shmueli (2007; http://arxiv.org/pdf/0710.5670.pdf), here is a proposal for generating the poisson random vector with the covariance matrix.

```{r poisson, echo=TRUE, eval=TRUE}
####
##  Define function
####
# Generate a p-dimensional Poisson
# p = the dimension of the distribution
# samples = the number of observations
# R = correlation matrix p X p
# lambda = rate vector p X 1
library(MASS)
GenerateMultivariatePoisson<-function(pD, samples, R, lambda){
  normal_mu=rep(0, pD)
  normal = mvrnorm(samples, normal_mu, R)
  pois = normal
  p=pnorm(normal)
  for (s in 1:pD){pois[s]=qpois(p[s], lambda[s])}
  return(pois)
}

####
##  Example
####
pD = 2
samples = 1
R = matrix(data = c(1,0.1,
                    0.8,1), ncol=2, nrow=2)
lambda = c(0.8, 0.3)
GenerateMultivariatePoisson(pD = pD, samples = samples, R = R, lambda = lambda)

```
